%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sai Srikanth Raju}{Rudraraju}{ 
\href{mailto:dd367@cornell.edu}{r.saisrikanthraju@gmail.com} | +91 9154-667-667
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Keshav Memorial Institute of Technology}
\descript{B.tech in Computer Science}
\location{Hyderabad \\ CGPA:7.5}
\sectionsep


\descript{Intermediate}
\location{ May 2013 | Hyderabad}
M.P.C \\
Narayana Junior College \\

\location{ Percentage 92}
\sectionsep
\descript{SSC}
\location{ May 2011 | Hyderabad}
M.P.C \\
Bhashyam Public School \\

\location{ Percentage 94}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{UNDERGRADUATE:1-4 sem.}
Computer Language \\
Digital Logic Design \\
Data Structures \\
Compiler Design \\
Cloud Computing \\
D.B.M.S\\
\sectionsep

\subsection{Undergraduate:4-8 sem.}
Information Retrieval \\
Operating Systems \\
Embedded Systems\\
Linux Programming \\
Big Data Analytics \\
Software Engineering\\

Web Technologies\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{technical Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   C \textbullet{} mySQL \textbullet{} HTML \\
 Python \textbullet{} JavaScript.  \\ 
 \sectionsep
\location{Over 1000 lines:}
Bootstrap \textbullet{} R \textbullet{} CSS \textbullet{} php\\
OpenCV \\
\sectionsep
\location{Familiar:}
selenium tool.    \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}

\runsubsection{sentiment analysis}
\descript{| Major Project }

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item The Twitter data is fetched using spring-xd Server, which is stored in HDFS. 
This is fed to the Sentiment Analysis engine built using python.  This generated score is then fed to the visualization framework which builds using JavaScript to create meaningful charts.
\item  Lexicon based approach is used to calculate the sentiments of the tweets and score is generated for each tweet.
\item  This generated score is then fed to the visualization framework which builds using JavaScript to create meaningful charts.
\end{tightemize}
\sectionsep

\runsubsection{easySRT}
\descript{| Mini Project }

\begin{tightemize}
\item  I have developed a python application which crawls the web and obtains subtitles for the user desired movie by automatically fetching it with just two clicks, making the work of the user easy.


\end{tightemize}
\sectionsep

\runsubsection{ATTENDANCE registrar}
\descript{| computer vision}

\begin{tightemize}
\item I have developed an application which uses computer vision (OpenCV) to record the attendance of students.
\item A model gets constructed based on the input images of the students. 
\item This model recognizes the student when he stands in front of the camera and marks down his attendance.
\end{tightemize}
\sectionsep
\sectionsep

\runsubsection{website}


\begin{tightemize}
\item I have developed a personal website for a neurosurgeon using HTML, CSS, JavaScript and Bootstrap. 
\item I have portrayed his skills and research work, portfolio, credentials and personal information.



\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{strengths} 
\sectionsep

\begin{tightemize}
\item Ability to work in team as well as individual.
\item Getting things done. 



\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies} 
\sectionsep

\begin{tightemize}
\item Internet saavy.
\item Read novels.
\item Learning about technological advancements. 
\item Weekend drives. 



\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}